Automating the Ontological Argument

### 2015-12-11 Papers/InProgress/IJCAI/paper.tex
Figures added
added formalization with improved notation

@@

\section{Introduction}
G\"{o}del's ontological argument for the existence of God is frequently
presented as a masterpiece argument in metaphysics. A huge body of
literature is available which discusses G\"{o}del's original work and/or
subsequent variants of it.

@@

\section{Intuitive Inconsistency Argument}
\subsection{LEO-II's Inaccessible Inconsistency Proof}
Tell the story (here or earlier). Show parts of LEO proof.  Inaccessible, but relevant knowledge
is contained.

@@

>>>>

\usepackage{graphicx}

@@

\section{Introduction}
G\"{o}del's ontological argument for the existence of God is frequently
presented as a masterpiece argument in metaphysics. A large body of
literature is available which discusses G\"{o}del's original work and/or
subsequent variants of it.

@@

\section{Intuitive Inconsistency Argument}
\subsection{LEO-II's Inaccessible Inconsistency Proof}
Tell the story (here or earlier). Show parts of LEO proof.  Inaccessible, but relevant knowledge
is contained.
\begin{figure*}
\centerline{\includegraphics[width=\textwidth]{./Images/LEO-Proof.png}}
\caption{Primitive substitution in LEO-II generates candidates for the
empty property.} \label{LEO-Proof}
\end{figure*}
LEO-II's resolution proof is human unintuitive. However, it contained
relevant hints to the empty property (cf. Fig.~\ref{LEO-Proof}).

@@

\subsection{Mapping to Gödel's Script}
\begin{figure*}
\centerline{\includegraphics[width=\textwidth]{./Images/Manuscript2.png}}
\caption{Sources of Inconsistence in G\"{o}del's proof script.} \label{GoedelScript}
\end{figure*}
